Modal type theory based on the intuitionistic epistemic logic

### 2018-01-25 article.tex
added some fixes

  i) For $\beta$-reduction

@@

2)

@@

ii) For $\eta$-reduction.

1) $[\![\vdash {\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N : {\bf }K A ]\!] = [\![\vdash {\bf pure \:} N : {\bf K A}]\!]$.

@@

\begin{defin}
  Let us define an endofunctor $\mathcal{K} : \mathcal{C}(\lambda) \to \mathcal{C}(\lambda)$, such that:

1) ${\bf K} : A \mapsto {\bf K}A$;

2) ${\bf K} : [x,M] \in Hom_{\mathcal{C}(\lambda)}(A,B) \mapsto \text{fmap } f = [y, {\bf let \: pure \:} x = y {\: \bf in \:} M] \in Hom_{\mathcal{C}(\lambda)}({\bf K} A, {\bf K} B)$.

@@

  Let $[p, \langle {\bf pure \:} (\pi_1 p), \pi_2 p \rangle] \in Hom_{\mathcal{C}(\lambda)}(A \times {\bf K}B, {\bf K}A \times {\bf K}B)$.

>>>>

@@

2) $[\![\vdash {\bf let \: pure \:} \underline{\quad} = \underline{\quad} {\: \bf in \:} N : {\bf }K A ]\!] = [\![\vdash {\bf pure \:} N : {\bf K A}]\!]$.

3)

@@

@@

\begin{defin}
  Let us define an endofunctor $\mathcal{K} : \mathcal{C}(\lambda) \to \mathcal{C}(\lambda)$, such that
forall $[x,M] \in Hom_{\mathcal{C}(\lambda)}(A,B), {\bf K}([x,M]) = [y, {\bf let \: pure \:} x = y {\: \bf in \:} M] \in Hom_{\mathcal{C}(\lambda)}({\bf K} A, {\bf K} B)$ (denotation: $\text{fmap } f$ for an arbitrary arrow $f$).

@@

  Let $[p, \langle {\bf pure \:} (\pi_1 p), \pi_2 p \rangle] \in Hom_{\mathcal{C}(\lambda)}(A \times {\bf K}B, {\bf K}(A \times B))$.
